A perfect storm and the natural endowments of trade-enabling infrastructure

### 2024-04-19 Slides/20min/20min.Rmd
Update slides

.pull-left[
- Link Lives 
- Individual-level data for the years 1787, 1801, 1834, 1845, 1860, 1870, 1890 and 1901 
- From this: Parish level population counts + occupations 
- New procedure to automatically make [HISCO labels](#hisco)

@@

![dag](Figures/dag_mechanism.png)
*DAG of the suggested mechanism* 
]

@@

---
name: other-results
# Conclusion 
.pull-left[
- **RQ:** How are we affected by geography? Does infrastructure cause development?
- Storm led to a channel and improved connectivity in 1834
- The population grew 22 percent in a generation in affected parishes 
- Population growth carried by trade and adaptation
- Intrinsic growth (fertility), fishing and manufacturing
]

@@

.pull-right[
**Moving forward**
- Quantifying institutions and secondary infrastructure
- Your comments!

<br>
```{r echo=FALSE, out.width="60%", fig.align='center'}
knitr::include_graphics("Figures/Morsoe.jpg")
```
*Oven from Morsø Iron foundry. Founded in a Limfjord Market town with British coal and Swedish iron in 1853*
]

>>>>

.pull-left[
- Link Lives 
- Individual-level data for the years 1787, 1801, 1834, 1845, 1860, 1870, 1890 and 1901 
- From this: Parish level population counts + occupations 
- New procedure to automatically make [HISCO labels](#hisco) - [OccCANINE](https://github.com/christianvedels/OccCANINE)

@@

![dag](Figures/dag_mechanism.png)
]

@@

---
name: other-results
# Conclusion 
.pull-left[
- **RQ:** How are we affected by geography? Does infrastructure cause development?
- Storm led to a channel and improved connectivity in 1834
- The population grew 24 percent in a generation in affected parishes 
- Population growth carried by trade and adaptation
- Intrinsic growth (fertility), fishing and manufacturing
]

@@

.pull-right[

![Map2](Figures/Map2.png)
```{r echo=FALSE, out.width="60%", fig.align='center'}
knitr::include_graphics("Figures/Morsoe.jpg")
```
*Oven from Morsø Iron foundry. Founded in a Limfjord Market town with British coal and Swedish/Norwegian iron in 1853*
]
